Bayesian statistics and swine flu

### 2009-09-25 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@417 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\comment{
<<setup,fig=false>>=
options(SweaveHooks=list(fig=function() par(mar=c(2.5,2.5,0.1,0.1), mgp=c(1.5, 0.5, 0), cex=0.6)), width=54, digits=3)
# source in all the R files
library(pandemic)
@
}

@@

\begin{frame}[fragile]
\frametitle{Simulated data}
<<echo=false,fig=false>>=
options(width=60)
@
<<simData,echo=true,fig=false>>=

data = simEpidemic(params, delta=50, days=42)

table(data$observedType)
@
<<fig=false>>=
toshow = NULL
for(Dshow in levels(data$observedType))
	toshow = c(toshow, which(data$observedType==Dshow)[1:2])
toshow = na.omit(toshow)	
#$
@
<<simData2,echo=true,fig=false>>=
data[toshow,-c(1,7)]
@

@@

\begin{frame}[fragile]
\frametitle{Fitting the model}
(to the simulated data)
<<mcmcResults,echo=true,fig=false>>=
scale = mcmcScale(params, 0.075,minScale = 0.05 )
paramSample = mcmcPandemic(data,params,priors,sigma=scale,runs=500, thin = 10)

dim(paramSample)
colnames(paramSample)
@
\end{frame}

@@

\begin{frame}
\frametitle{Hospitalization rate}
<<fatalityAgeGraph>>=
ageColsS = grep("^ageProbs.S.prob.[[:digit:]]+$", colnames(paramSample), value=T)

@@

\begin{frame}[fragile]
\frametitle{Hospital demand}
<<hospLoad,echo=T>>=
# generate hospital times
hospSample = simHospitals(paramSample , Ndays=80, 
	NinfectionsPerDay=20 )

# graph hospital times
plotHospitals(hospSample)
abline(h=20)
@
\end{frame}

@@

# graph hospital times
plotHospitals(hospSample2)
lines(Ninfect)
@
}
\end{frame}

>>>>

\comment{
<<setup,fig=false>>=
options(SweaveHooks=list(fig=function() par(mar=c(2.5,2.5,0.1,0.1), mgp=c(1.5, 0.5, 0), cex=0.6)), width=54, digits=3)
# source in all the R files
library(pandemic)
doSims=F
@
}

@@

\begin{frame}[fragile]
\frametitle{Simulated data}
<<echo=false,fig=false>>=
options(width=60)
if(doSims){
data = simEpidemic(params, delta=50, days=42)
} else{
load("results.RData")
}
@
\verb!data = simEpidemic(params, delta=50, days=42)!
<<simData,echo=true,fig=false>>=
table(data$observedType)
@
<<fig=false>>=
toshow = NULL
for(Dshow in levels(data$observedType))
	toshow = c(toshow, which(data$observedType==Dshow)[1:2])
toshow = na.omit(toshow)	
#$
@
<<simData2,echo=true,fig=false>>=
data[toshow,-c(1,7)]
@

@@

\begin{frame}[fragile]
\frametitle{Fitting the model}
(to the simulated data)
<<mcmcResults,echo=true,fig=false>>=
scale = mcmcScale(params, 0.075,minScale = 0.05 )
if(doSims){
	paramSample = mcmcPandemic(data,params,priors,sigma=scale,runs=500, thin = 10)
}
dim(paramSample)
colnames(paramSample)
@
\end{frame}

@@

\begin{frame}
\frametitle{Hospitalization rate}
<<hospitalAgeGraph>>=
ageColsS = grep("^ageProbs.S.prob.[[:digit:]]+$", colnames(paramSample), value=T)

@@

\begin{frame}[fragile]
\frametitle{Hospital demand}
<<hospLoad,echo=T>>=
# generate hospital times
if(doSims) {
hospSample = simHospitals(paramSample , Ndays=80, 
	NinfectionsPerDay=20 )
}

# graph hospital times
plotHospitals(hospSample)
abline(h=20/5)
@
\end{frame}

@@

# graph hospital times
plotHospitals(hospSample2)
lines(Ninfect/5)
@
}
\end{frame}
